Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-02 presentation-plan/Plan_presentation_monday.tex

%\begin{itemize}
%	\item STRIPS \cite{fikes1971strips}
%\end{itemize}
%
%\subsubsection{STRIPS}
%
%STRIPS~\cite{fikes1971strips} is a influential method of defining planning
%problems.
%
%Take for example~\ref{fig:strips}. R is the robot, B and C are two objects at
%places a, b and c. The goal is to achieve the configuration such that B is at
%place k and in which C is not at place c. The robot can move to an object and
%it can push objects to another position.
%
%\begin{figure}[htb]%
%\includegraphics[width=0.8\columnwidth]{strips-example.pdf}%
%\caption{Configuration of objects and robot for example problem (Figure from~\cite{fikes1971strips})}%
%\label{fig:strips}%
%\end{figure}
%
%The goal could be written as
%
%\[(\exists s) [ AT(B,k,s) \land \neg AT(C,c,s) ]\]
%
%If we find an instance of s, the problem is solved.
%
%STRIPS also defines operators. In this instance examples can be \texttt{goto}
%and \texttt{push}.
%
%\begin{description}
%	\item[push(u,x,y)] Robot pushes object \texttt{u} from \texttt{x} to
%		position \texttt{y}
%	\begin{description}
%		\item[Precondition:] $(\exists s) [AT(u,x,s) \land ATR(x,s)]$
%		\item[Delete list:] $\{AT(u,x,s), ATR(x,s)\}$
%		\item[Add list:] $\{AT(u,y,push'(u,x,y,s^*)), ATR(y,push'(u,x,y,s^*))\}$
%	\end{description}
%	\item[goto(x,y)] Robot goes from place \texttt{x} to \texttt{y}
%	\begin{description}
%		\item[Precondition:] $(\exists s) [ATR(x,s)]$
%		\item[Delete list:] $\{ATR(x,s)\}$
%		\item[Add list:] $\{ATR(y,goto'(x,y,s^*))\}$
%	\end{description}
%\end{description}
%
%The initial world model can be described by:
%
%\[
%	s_0 : \{ ATR(a,x_0), AT(B,b,s_0), AT(C,c,s_0) \}
%\]
%
%Besides that there is a global requirement that two blocks cannot be at the
%same position at any time.
%
%\paragraph{Problems}
%
%\begin{itemize}
%	\item How to efficiently store nodes (states) of the
%		world.~\cite{fikes1971strips}
%	\item Arbitrary STRIPS planning problem is a PSPACE complete
%		problem.~\cite{mcallester1991systematic}
%	\item Extremely limited in scope of planning problems and complexity of
%		problems it can solve.~\cite{fikes1994strips}
%	\item When executing a plan in a real environment, the resulting state
%		of the world is often different from the state expected by the
%		planner.~\cite{fikes1994strips}
%\end{itemize}
%
%\paragraph{Strengths}
%
%\begin{itemize}
%	\item Formed the basis for many extensions
%
%\end{itemize}

@@

\subsection{FF-replan (I)}

>>>>

@@

\subsection{FF-replan \cite{FFReplan}}
%Define the problem considering probabilistic and deterministic planning

\subsubsection{Problem definition} 
Probabilistic planning is naturally formulated using Markov Decision Processes. These probabilistic planners focus on the entire state space. Deterministic planning has developed heuristic funtions enabling exploration of restricted portions of the state space enroute to the goal state. This enables the planner to account for unexpected states rather than ending up in a dead-end. MDP's had been the standard in planning algorithms [FOR HOW LONG]? However by relying on search and current available processing power, deterministic planners function with enormous speed and efficiency. This has been a motivation for combining deterministic and probabilistic planners in the planning communities.

\subsubsection{Motivation for the solution}
FF-Replan is an action selection algorithm for online planning in probabilistic domains. An important notice is that the authors of the paper merely hoped to promote cross-fertilization of deterministic planning techniques in probabilistic planning. The basics of the FF-replan algorithm are simple and are valuable mostly because of the speed and efficiency introduced by relying on search.  It determinizes the input domain, removing all probabilistic information from the problem and synthesizes a plan. During the execution of this plan, should an unexpected state occur, the planner replans in the same determinization.

\subsubsection{Details of the solution}
FF-Replan used two approaches to determinize the input domain. The first is single-outcome determinization which selects one outcome for each probabilistic construct. The heuristics determine the performance of the planner and should be chosen with care. The second approach uses an all-outcomes determinization and considers every probabilistic outcome as a distinct deterministic action. FF-Replan than generates one action for each effect (recursively). This ensures that an action in a state is chosen that is the first action of a sequential plan with non-zero probability of reaching the goal.

The planner maintains a partial state-action mapping using a hash-table. It determinizes the states and synthesizes a plan using FF and then places the state-action sequence in the table.

It doesn't deal with quantified goals but it picks an arbitrary grounded form of any existential goal.

\subsubsection{Succes of the solution}
The planner performs strong on Logistic style domains and dead-end free domains. It performs very fast by relying on search.

\subsubsection{Shortcomings of the solution}
\begin{enumerate}
	\item When no info about the probabilistic effects is provided, all effects are treated as equal. The FF-replan then doesn't attempt to avoid actions that can potentially end up in a dead end or away from the goal.
	\item  The planner only works well if the outcomes are likely. It might behave poorly in a very fluctuating behavioural environment. 
	\item The partial state-action policy does not guarantee quality. It may actually loop forever.  
	\item Picking arbitrary grounded forms of the goal may end up being unreachable or a lot more expensive to reach.
	\item The single outcome heuristic does not select the dead end outcomes and thus is completely unaware of them.  
\end{enumerate}

\subsubsection{Points of improvement}
\begin{enumerate}
	\item
	\item 
	\item Adaptively repair the partial policy 
	\item Sampling of the grounded goals and testing with a relaxed reachability analysis
	\item This is solved by using the all-outcomes approach
	\item It does not look ahead, but only adjusts when something unexpected has occured

	\item Investigate incremental planning approaches that leverage the most deterministic plan
\end{enumerate}

\subsubsection{Things to look into}
\begin{itemize}
	\item How is the exploding block domain currently tackled as during 2004 and 2006 no one really was able to solve it?
	\item Is the planning time still a problem as much as it proved to be then with the bigger domains?
	\item Using hindsight optimization might be more realistic as it is less optimistic. It will eventuall increase the process time, but increase the robustness of the system. 
	\item Using a look ahead policy enables the planner to avoid dead ends, it however does not avoid cycles.
\end{itemize}
